---
title: 'Grip Task #2'
author: "Insha Shah"
date: "6/17/2021"
output: html_document
---

Topic: Prediction Using Unsupervised Machine Learning

Problem: From the ‘Iris’ dataset, predict the optimum number of clusters 
and represent it visually. 

Load the required packages
```{r}
library(cluster)
```

Load the Iris Dataset
```{r}
data<-iris[,-5]
head(iris)
```

Finding the optimum number of clusters for k-means classification
```{r}
set.seed(123)
tot_within_ss<- vector(mode = "character", length = 10)
for (i in 1:10) {
  iriscluster<- kmeans(data[,1:4], centers = i, nstart = 20)
  tot_within_ss[i] <- iriscluster$tot.withinss
}
```

Plotting the results onto a line graph
```{r}
plot(1:10, tot_within_ss, type = "b", pch = 19)
```

The optimum clusters is where the elbow occurs.
Thus, the number of clusters is '3'.

Applying Kmeans to the dataset
```{r}
set.seed(123)
kmean <- kmeans(data[,1:4], centers = 3, iter.max = 300)
kmean
```

Confusion Matrix-Comparing the predicted clusters with the original data
```{r}
table(kmean$cluster, iris$Species)
```
All 50 Setosa are correctly classified as Setosa.
Out of 62 Versicolor,48 are correctly classified as Versicolor and 14 are classified as Virginica
Out of 38 Virginica, 36 are correctly classified as Virginica and 2 are classified as Versicolor 

Visualizing the cluster - First two columns
```{r}
clusplot(data[,c(1,2)], 
         kmean$cluster,
         shade = T, 
         color = T,
         lines = 0,
         span = T,
         main = "Cluster Iris",
         xlab = "Sepal Length",
         ylab = "Sepal Width", 
         plotchar = T)
```